Age-related changes in plant growth and traits

### 2016-06-06 scripts/Accessory_figs_20160218.Rmd
testing seedcost categories to make sure no unexpected zeros

>>>>

#fixed = BOLE, GRBU, PUTU,

#nearly fixed = EPMI, PELA, LEES
check <- subset(SummarySpp[["mean"]],species=="BOLE")
check$seed_size
check$embryo_endo_size
check$seed_costs
check$prepollen_costs
check$pack_disp_costs
check$pack_disp_costs_plus
check$pack_disp_early_costs
check$seed_early_costs

parts <- subset(PartsSummary,species=="COER")
parts

invest <- subset(InvestmentByPart,species=="PUTU"&part=="flower_petals")
invest

invest_ind <- subset(InvestmentByPart,individual=="PUTU_152")

ind <- subset(SummaryInd, species=="GRBU"&seed_count>0)
check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_early_costs,propagule_per_seed,seed_costs)

View(check3)

plot(seed_costs ~pack_disp_costs,check3)
points(seed_costs ~ propagule_per_seed,check3,col="red",pch=16)
text(seed_costs ~pack_disp_costs,check3,label=individual)
